---
title: "LMS results"
output: word_document
---

```{r warning=FALSE, message=FALSE, echo=FALSE}
rm(list=ls())
require(moonBook)
library(lme4)
library(pROC)
library(caret)
data <- read.csv("LMS_data_r.csv")
```


# 1. result for R2


```{r message=TRUE, echo=FALSE}
ResVar = "malignancy"
Model = as.formula(paste(ResVar, "~shape_R2+margin_R2+hemorrhage_R2+T2dark_R2+
                     necrosis_R2+ADC_R2+RCR_R2"))
```


## 1-1. cross table analysis


```{r, echo=FALSE}
table <- mytable(Model,data=data, digits= 3, show.total=TRUE)
table
```


## 1-2. logistic regression model with OR calculation for qualitative features


```{r, echo=FALSE}
ORtable=function(x,digits=4){
    suppressMessages(a<-confint(x))
    result=data.frame(exp(coef(x)),exp(a))
    result=round(result,digits)
    result=cbind(result,round(summary(x)$coefficient[,4],3))
    colnames(result)=c("OR","2.5%","97.5%","p")
    result
}

feature_qual = as.formula(paste(ResVar, "~shape_R2+margin_R2+T2dark_R2+hemorrhage_R2+
                     necrosis_R2"))
logistic_qual = glm(feature_qual, data = data, family = binomial)
#summary(logistic_qual)
#ORtable(logistic_qual)
ORplot(logistic_qual,type=2,show.OR=TRUE,show.CI=TRUE,
       main="Odds Ratios of LMS from MRI Features ") 
```


## 1-3. ROC curve for LR model with qualitative features


```{r, message=FALSE, echo=FALSE}

feature_qual = as.formula(paste(ResVar, "~shape_R2+T2dark_R2+necrosis_R2"))
logistic_qual = glm(feature_qual, data = data, family = binomial)
Log_odds=predict(logistic_qual, newdata= data)
Prob = predict(logistic_qual, newdata= data, type='response')

PREDICTED_C = ifelse(Prob > 0.338 , 1 , 0)
PREDICTED_C = factor(PREDICTED_C,levels = c(0,1))
data$malignancy = factor(data$malignancy, levels = c(0,1))
#confusionMatrix(PREDICTED_C,data$malignancy)
ROC = roc(data$malignancy, Prob)
#plot.roc(ROC, col="red", print.auc=TRUE, print.auc.adj=c(1.11,1.2),
#         print.thres=TRUE, print.thres.adj=c(0.3,-1.0), legacy.axes = TRUE)


feature_adc = as.formula(paste(ResVar, "~shape_R2+T2dark_R2+necrosis_R2+ADC_R2"))
logistic_adc = glm(feature_adc, data = data, family = binomial)
Prob2 = predict(logistic_adc, newdata= data, type='response')
ROC_ADC = roc(data$malignancy, Prob2)


feature_rcr = as.formula(paste(ResVar, "~shape_R2+T2dark_R2+necrosis_R2+RCR_R2"))
logistic_rcr = glm(feature_rcr, data = data, family = binomial)
Prob3 = predict(logistic_rcr, newdata= data, type='response')
ROC_RCR = roc(data$malignancy, Prob3)


library(ggplot2)
#roc.list <- roc(malignancy ~ shape_R2+ADC_R2+RCR_R2, data=data)
#roc.list[1] <- ROC

ROC.list <- list(ROC,ROC_ADC,ROC_RCR)
ll = round(sapply(ROC.list, auc), 3)
ll = paste("AUC of", c("qualitative only","qualitative + ADC","qualitative + RCR"), "=", ll)

g.list <- ggroc(ROC.list, aes=c("color"), legacy.axes = TRUE)+
    geom_line(size = 1, alpha = 0.7)+ theme_bw() +
    theme(legend.justification="bottom",legend.position="right",panel.border = element_blank(), panel.grid.major = element_blank(),panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))+
    scale_color_manual(name="Reader 1", labels=c("qualitative only","qualitative + ADC","qualitative + RCR"),values=c("red","black","blue"))+
    annotate("text", x=0.75, y=0.15, label=ll[1], col='red') + 
    annotate("text", x=0.75, y=0.1, label=ll[2], col='black') + 
    annotate("text", x=0.75, y=0.05, label=ll[3], col='blue')
g.list 

#ggsave("reader1.tiff", plot = print(g.list), dpi=200, dev='tiff', height=8.27/1.5, width=11.69/1.5, units="in")

```

```{r, message=FALSE, echo=FALSE}
ci.auc(ROC_RCR)
```



## 1-4. ROC curve using ADC only


```{r, message=FALSE, echo=FALSE}

ROC_adc = roc(data$malignancy, data$ADC_R2)
plot.roc(ROC_adc, col="red", print.auc=TRUE, print.auc.adj=c(1.11,1.2),
         print.thres=TRUE, print.thres.adj=c(0.3,-1.0), legacy.axes = TRUE)
```


## 1-5. ROC curve for RCR only


```{r, message=FALSE, echo=FALSE}

ROC_rcr = roc(data$malignancy, data$RCR_R2)
plot.roc(ROC_rcr, col="red", print.auc=TRUE, print.auc.adj=c(1.11,1.2),
         print.thres=TRUE, print.thres.adj=c(0.3,-1.0), legacy.axes = TRUE)
```


## 1-6. ROC curve of LR model: qualitative features + ADC


```{r, message=FALSE, echo=FALSE}
feature_adc = as.formula(paste(ResVar, "~shape_R2+margin_R2+T2dark_R2+
                     necrosis_R2+ADC_R2"))
logistic_adc = glm(feature_adc, data = data, family = binomial)
Log_odds=predict(logistic_adc, newdata= data)
Prob = predict(logistic_adc, newdata= data, type='response')

PREDICTED_C = ifelse(Prob > 0.5 , 1 , 0)
PREDICTED_C = factor(PREDICTED_C,levels = c(0,1))
#confusionMatrix(PREDICTED_C,data$malignancy)
ROC_ADC = roc(data$malignancy, Prob)
plot.roc(ROC_ADC, col="red", print.auc=TRUE, print.auc.adj=c(1.11,1.2),
         print.thres=TRUE, print.thres.adj=c(0.3,-1.0), legacy.axes = TRUE)
```


## 1-7. ROC curve of LR model: qualitative features + RCR


```{r, message=FALSE, echo=FALSE}
feature_rcr = as.formula(paste(ResVar, "~shape_R2+margin_R2+T2dark_R2+
                     necrosis_R2+RCR_R2"))
logistic_rcr = glm(feature_rcr, data = data, family = binomial)
Log_odds=predict(logistic_rcr, newdata= data)
Prob = predict(logistic_rcr, newdata= data, type='response')

PREDICTED_C = ifelse(Prob > 0.5 , 1 , 0)
PREDICTED_C = factor(PREDICTED_C,levels = c(0,1))
#confusionMatrix(PREDICTED_C,data$malignancy)
ROC_RCR = roc(data$malignancy, Prob)
plot.roc(ROC_RCR, col="red", print.auc=TRUE, print.auc.adj=c(1.11,1.2),
         print.thres=TRUE, print.thres.adj=c(0.3,1.0), legacy.axes = TRUE)
```


## 1-8. Comparison of ROC: qualitative features vs. qualitative features + RCR


```{r}
roc.test(ROC,ROC_ADC)
```


## 1-9. Comparison of ROC: qualitative features + ADC vs. qualitative features + RCR


```{r}
roc.test(ROC_ADC,ROC_RCR)
```


***   
   
   
# 2. result for K


## 2-1. cross table analysis


```{r, echo=FALSE}
ResVar = "malignancy"
Model = as.formula(paste(ResVar, "~shape_K+margin_K+hemorrhage_K+T2dark_K+
                     necrosis_K+ADC_K+RCR_K"))

## cross table analysis
table <- mytable(Model,data=data, show.total=TRUE)
table
```


## 2-2. logistic regression model with OR calculation for qualitative features


```{r, echo=FALSE}
ORtable=function(x,digits=4){
    suppressMessages(a<-confint(x))
    result=data.frame(exp(coef(x)),exp(a))
    result=round(result,digits)
    result=cbind(result,round(summary(x)$coefficient[,4],3))
    colnames(result)=c("OR","2.5%","97.5%","p")
    result
}

feature_qual = as.formula(paste(ResVar, "~shape_K+margin_K+T2dark_K+
                     necrosis_K"))
logistic_qual = glm(feature_qual, data = data, family = binomial)
#summary(logistic_qual)
#ORtable(logistic_qual)
ORplot(logistic_qual,type=2,show.OR=TRUE,show.CI=TRUE,
       main="Odds Ratios of Qualitative Features") 
```


## 2-3. ROC curve for LR model with qualitative features


```{r, message=FALSE, echo=FALSE}

feature_qual = as.formula(paste(ResVar, "~shape_K+T2dark_K+necrosis_K"))
logistic_qual = glm(feature_qual, data = data, family = binomial)
Log_odds=predict(logistic_qual, newdata= data)
Prob = predict(logistic_qual, newdata= data, type='response')

PREDICTED_C = ifelse(Prob > 0.338 , 1 , 0)
PREDICTED_C = factor(PREDICTED_C,levels = c(0,1))
data$malignancy = factor(data$malignancy, levels = c(0,1))
#confusionMatrix(PREDICTED_C,data$malignancy)
ROC = roc(data$malignancy, Prob)
#plot.roc(ROC, col="red", print.auc=TRUE, print.auc.adj=c(1.11,1.2),
#         print.thres=TRUE, print.thres.adj=c(0.3,-1.0), legacy.axes = TRUE)


feature_adc = as.formula(paste(ResVar, "~shape_K+T2dark_K+necrosis_K+ADC_K"))
logistic_adc = glm(feature_adc, data = data, family = binomial)
Prob2 = predict(logistic_adc, newdata= data, type='response')
ROC_ADC = roc(data$malignancy, Prob2)


feature_rcr = as.formula(paste(ResVar, "~shape_K+T2dark_K+necrosis_K+ADC_K+RCR_K"))
logistic_rcr = glm(feature_rcr, data = data, family = binomial)
Prob3 = predict(logistic_rcr, newdata= data, type='response')
ROC_RCR = roc(data$malignancy, Prob3)



ROC.list <- list(ROC,ROC_ADC,ROC_RCR)
ll = round(sapply(ROC.list, auc), 3)
ll = paste("AUC of", c("qualitative only","qualitative + ADC","qualitative + RCR"), "=", ll)

g.list <- ggroc(ROC.list, aes=c("color"), legacy.axes = TRUE)+
    geom_line(size = 1, alpha = 0.7)+ theme_bw() +
    theme(legend.justification="bottom",legend.position="right",panel.border = element_blank(), panel.grid.major = element_blank(),panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))+
    scale_color_manual(name="Reader 2", labels=c("qualitative only","qualitative + ADC","qualitative + RCR"),values=c("red","black","blue"))+
    annotate("text", x=0.75, y=0.15, label=ll[1], col='red') + 
    annotate("text", x=0.75, y=0.1, label=ll[2], col='black') + 
    annotate("text", x=0.75, y=0.05, label=ll[3], col='blue')
g.list 

#ggsave("reader2.tiff", plot = print(g.list), dpi=200, dev='tiff', height=8.27/1.5, width=11.69/1.5, units="in")
```


## 2-4. ROC curve using ADC only


```{r, message=FALSE, echo=FALSE}

ROC_adc = roc(data$malignancy, data$ADC_K)
plot.roc(ROC_adc, col="red", print.auc=TRUE, print.auc.adj=c(1.11,1.2),
         print.thres=TRUE, print.thres.adj=c(0.3,-1.0), legacy.axes = TRUE)
```


## 2-5. ROC curve for RCR only


```{r, message=FALSE, echo=FALSE}

ROC_rcr = roc(data$malignancy, data$RCR_K)
plot.roc(ROC_rcr, col="red", print.auc=TRUE, print.auc.adj=c(1.11,1.2),
         print.thres=TRUE, print.thres.adj=c(0.3,-1.0), legacy.axes = TRUE)
```


## 2-6. ROC curve of LR model: qualitative features + ADC


```{r, message=FALSE, echo=FALSE}
feature_adc = as.formula(paste(ResVar, "~shape_K+margin_K+T2dark_K+
                     necrosis_K+ADC_K"))
logistic_adc = glm(feature_adc, data = data, family = binomial)
Log_odds=predict(logistic_adc, newdata= data)
Prob = predict(logistic_adc, newdata= data, type='response')

PREDICTED_C = ifelse(Prob > 0.5 , 1 , 0)
PREDICTED_C = factor(PREDICTED_C,levels = c(0,1))
#confusionMatrix(PREDICTED_C,data$malignancy)
ROC_ADC = roc(data$malignancy, Prob)
plot.roc(ROC_ADC, col="red", print.auc=TRUE, print.auc.adj=c(1.11,1.2),
         print.thres=TRUE, print.thres.adj=c(0.3,-1.0), legacy.axes = TRUE)
```


## 2-7. ROC curve of LR model: qualitative features + RCR


```{r, message=FALSE, echo=FALSE}
feature_rcr = as.formula(paste(ResVar, "~shape_K+margin_K+T2dark_K+
                     necrosis_K+RCR_K"))
logistic_rcr = glm(feature_rcr, data = data, family = binomial)
Log_odds=predict(logistic_rcr, newdata= data)
Prob = predict(logistic_rcr, newdata= data, type='response')

PREDICTED_C = ifelse(Prob > 0.5 , 1 , 0)
PREDICTED_C = factor(PREDICTED_C,levels = c(0,1))
#confusionMatrix(PREDICTED_C,data$malignancy)
ROC_RCR = roc(data$malignancy, Prob)
plot.roc(ROC_RCR, col="red", print.auc=TRUE, print.auc.adj=c(1.11,1.2),
         print.thres=TRUE, print.thres.adj=c(0.3,-1.0), legacy.axes = TRUE)
```


## 2-8. Comparison of ROC: qualitative features vs. qualitative features + RCR


```{r}
roc.test(ROC,ROC_ADC)
```


## 2-9. Comparison of ROC: qualitative features + ADC vs. qualitative features + RCR


```{r}
roc.test(ROC_ADC,ROC_RCR)
```

```{r}
ci.auc(ROC)
```


